# Catalog, Soil and Ground motion intensity

## Catalog Information
```{r catalog.info,echo=F,results='asis'}
  pandoc.table(as.data.frame(catalog),style='rmarkdown')
```

```{r function.rupture,echo=F,include=F}
if(nrow(catalog) > 1){
  catalog <- catalog[NumSegments>0,]
}else{
  catalog$NumSegments <- 1
}
out.sr <- list()
for(i in 1:nrow(catalog)){
  out.sr[[i]] <- rupture.polygon(Lon=catalog$Lon[i],
                                 Lat=catalog$Lat[i],
                                 Depth=catalog$FocalDepth[i],
                                 Length=catalog$Length[i],
                                 Width=catalog$Width[i],
                                 Azimuth=catalog$Azimuth[i], 
                                 DipAngle=catalog$DipAngle[i],
                                 DipAzi=catalog$DipAzimuth[i],
                                 segmentID=catalog$NumSegments[i])
}
sr <- SpatialPolygons(out.sr, proj4string=CRS('+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs'))
att.tb <- data.frame(segment=catalog$NumSegments)
rownames(att.tb) <- as.character(att.tb$segment)
rupture.srdf <- SpatialPolygonsDataFrame(sr,data=att.tb,match.ID=T)
```

## Soil Map
### Pre-made soil map

```{r Soil.Map, fig.width=12,fig.height=8,warning=F,cache=F,results='asis'}
if(include.GM & pre.made.GM.intensity){
  rst <- raster(Soil.raster)
  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'Soil')

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('Soil'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'Soil')
  m 
}else{
  cat('<span style="color:red">Sorry, man, did you forget to provide pre-made maps?</span>')
}
```

### Soil map from int file

```{r fp.based.soil.prepare, echo = FALSE, include =FALSE}
if(include.GM){
  GM.int.FP <- int.Hist[,.(lon,lat,value=Soil)]
  LongMin <- floor(min(GM.int.FP$lon))
  LongMax <- ceiling(max(GM.int.FP$lon))
  LatMin <- floor(min(GM.int.FP$lat))
  LatMax <- ceiling(max(GM.int.FP$lat))
  background <- raster(xmn = LongMin, xmx = LongMax,
                       ymn = LatMin, ymx = LatMax,
                       resolution = raster.res)
  grid.ctr <- GM.int.FP[,.(lon,lat)]
  rst <- rasterize(grid.ctr, background, fun = mean,
                   field = GM.int.FP[,.(value)])
  writeRaster(rst, filename = file.path(US.Eng.dir, data.dir,'maps',
                                        paste0(event.name,'soil.from.Footprint.',today,'.img')),
              format = 'HFA',overwrite = T)
}
```

```{r fp.based.soil.Map, fig.width=12,fig.height=8,warning=F}
if(include.GM){
  r.range <- c(minValue(rst), maxValue(rst))
  pal <- colorBin(palette = c('#E7E739','#006121'), 
                  domain = r.range, bins=6)
  leaflet()%>%
  addProviderTiles(provider = 'Stamen.TonerLite',
                  group = 'Toner Lite') %>%
  addTiles(group = 'OSM')%>%
  addProviderTiles(provider = 'MapQuestOpen.Aerial',group='Aerial')%>%
  addRasterImage(rst, colors = pal, opacity = 0.5, group = 'soil')%>%
  addPolygons(data=rupture.srdf, weight = 2, 
              fill=F, color = 'darkblue',
              popup=paste0('Segment: ',rupture.srdf$segment))%>%
  addLayersControl(baseGroups = c("Aerial","Toner Lite","OSM"), 
                   overlayGroups = c('soil'),
                   options = layersControlOptions(collapsed = FALSE))%>%
  addLegend(position = "bottomleft", pal = pal, 
            values = range(v), opacity = 1,
            title = 'Soil')
}
```

## Modeled MMI 

### Pre-made ground motion MMI 

```{r MMI.Map, fig.width=12,fig.height=8,warning=F,cache=F,results='asis'}
if(include.GM & pre.made.GM.intensity){
  rst <- raster(MMI.raster)

  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')
  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'MMI')

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('MMI'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'MMI')
  m 
}else{
  cat('<span style="color:red">Sorry, man, did you forget to provide pre-made maps?</span>')
}
```

### MMI map from EQSim footprint file

```{r fp.based.MMI.prepare, echo = FALSE, include =FALSE}
if(include.GM){
  GM.int.FP <- int.Hist[,.(lon,lat,value=MMI)]
  LongMin <- floor(min(GM.int.FP$lon))
  LongMax <- ceiling(max(GM.int.FP$lon))
  LatMin <- floor(min(GM.int.FP$lat))
  LatMax <- ceiling(max(GM.int.FP$lat))
  background <- raster(xmn = LongMin, xmx = LongMax,
                       ymn = LatMin, ymx = LatMax,
                       resolution = raster.res)
  grid.ctr <- GM.int.FP[,.(lon,lat)]
  rst <- rasterize(grid.ctr, background, fun = mean,
                   field = GM.int.FP[,.(value)])
  writeRaster(rst, filename = file.path(US.Eng.dir, data.dir,'maps',
                                        paste0(event.name,'MMI.from.Footprint.',today,'.img')),
              format = 'HFA',overwrite = T)
}
```

```{r fp.based.MMI.Map, fig.width=12,fig.height=8,warning=F}
if(include.GM){
  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'MMI')
  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('MMI'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'MMI')
  m 
}
```

## Modeled PGA 

### Pre-made raster map of PGA using contrived exposure

```{r PGA.Map, fig.width=12,fig.height=8,warning=F,cache=F,results='asis'}
if(include.GM & pre.made.GM.intensity){
  rst <- raster(PGA.raster)
  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'PGA')

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('PGA'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'PGA, g')
  m 
}else{
  cat('<span style="color:red">Sorry, man, did you forget to provide pre-made maps?</span>')
}
```

### PGA map based on EQSim footprint file

```{r fp.based.PGA.prepare, echo = FALSE, include =FALSE}
if(include.GM){
  GM.int.FP <- int.Hist[,.(lon,lat,value=PGA)]
  LongMin <- floor(min(GM.int.FP$lon))
  LongMax <- ceiling(max(GM.int.FP$lon))
  LatMin <- floor(min(GM.int.FP$lat))
  LatMax <- ceiling(max(GM.int.FP$lat))
  background <- raster(xmn = LongMin, xmx = LongMax,
                       ymn = LatMin, ymx = LatMax,
                       resolution = raster.res)
  grid.ctr <- GM.int.FP[,.(lon,lat)]
  rst <- rasterize(grid.ctr, background, fun = mean,
                   field = GM.int.FP[,.(value)])
  writeRaster(rst, filename = file.path(US.Eng.dir, data.dir,'maps',paste0(event.name,'PGA.from.Footprint.',today,'.img')),
              format = 'HFA',overwrite = T)
}
```

```{r fp.based.PGA.Map, fig.width=12,fig.height=8,warning=F}
if(include.GM){
  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'PGA')

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('PGA'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'PGA')
  m 
}
```

## Modeled Sa 0.3 sec 

### Pre-made raster map using contrived exposure

```{r SA03.Map, fig.width=12,fig.height=8,warning=F,cache=F,results='asis'}
if(include.GM & pre.made.GM.intensity){
  rst <- raster(SA03.raster)

  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'SA0.3')

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('SA0.3'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'SA0.3, g')
  m 
}else{
  cat('<span style="color:red">Sorry, man, did you forget to provide pre-made maps?</span>')
}
```

### Sa 0.3 map based on EQSim footprint file

```{r fp.based.SA03.prepare, echo = FALSE, include =FALSE}
if(include.GM){
  GM.int.FP <- int.Hist[,.(lon,lat,value=SA03)]
  LongMin <- floor(min(GM.int.FP$lon))
  LongMax <- ceiling(max(GM.int.FP$lon))
  LatMin <- floor(min(GM.int.FP$lat))
  LatMax <- ceiling(max(GM.int.FP$lat))
  background <- raster(xmn = LongMin, xmx = LongMax,
                       ymn = LatMin, ymx = LatMax,
                       resolution = raster.res)
  grid.ctr <- GM.int.FP[,.(lon,lat)]
  rst <- rasterize(grid.ctr, background, fun = mean,
                   field = GM.int.FP[,.(value)])
  writeRaster(rst, filename = file.path(US.Eng.dir, data.dir,'maps',paste0(event.name,'SA03.from.Footprint.',today,'.img')),
              format = 'HFA',overwrite = T)
}
```

```{r fp.based.SA03.Map, fig.width=12,fig.height=8,warning=F}
if(include.GM){
  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]

  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'SA03')

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('SA03'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'Sa 0.3s, g')
  m 
}
```

## Modeled Sa 1.0 sec 

### Pre-made Sa 1.0s map using contrived exposure

```{r SA1.Map, fig.width=12,fig.height=8,warning=F,cache=F,results='asis'}
if(include.GM & pre.made.GM.intensity){
  rst <- raster(SA1.raster)

  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'SA1')

  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('SA1'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'SA1, g')
  m 
}else{
  cat('<span style="color:red">Sorry, man, did you forget to provide pre-made maps?</span>')
}
```

### Sa 1.0s map based on EQSim footprint file

```{r fp.based.SA1.prepare, echo = FALSE, include =FALSE}
if(include.GM){
  GM.int.FP <- int.Hist[,.(lon,lat,value=SA1)]
  LongMin <- floor(min(GM.int.FP$lon))
  LongMax <- ceiling(max(GM.int.FP$lon))
  LatMin <- floor(min(GM.int.FP$lat))
  LatMax <- ceiling(max(GM.int.FP$lat))
  background <- raster(xmn = LongMin, xmx = LongMax,
                       ymn = LatMin, ymx = LatMax,
                       resolution = raster.res)
  grid.ctr <- GM.int.FP[,.(lon,lat)]
  rst <- rasterize(grid.ctr, background, fun = mean,
                   field = GM.int.FP[,.(value)])
  writeRaster(rst, filename = file.path(US.Eng.dir, data.dir,'maps',paste0(event.name,'SA1.from.Footprint.',today,'.img')),
              format = 'HFA',overwrite = T)
}
```

```{r fp.based.SA1.Map, fig.width=12,fig.height=8,warning=F}
if(include.GM){
  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'SA1')

  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('SA1'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'Sa 1.0s, g')
  m 
}
```

## Modeled Sa 3.0 sec 

### Pre-made raster using contrived exposure

```{r SA3.Map, fig.width=12,fig.height=8,warning=F,cache=F,results='asis'}
if(include.GM & pre.made.GM.intensity){
  rst <- raster(SA3.raster)

  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'SA3')

  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('SA3'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'SA3, g')
  m 
}else{
  cat('<span style="color:red">Sorry, man, did you forget to provide pre-made maps?</span>')
}
```

### Sa 3.0s map based on EQSim footprint file

```{r fp.based.SA3.prepare, echo = FALSE, include =FALSE}
if(include.GM){
GM.int.FP <- int.Hist[,.(lon,lat,value=SA3)]
LongMin <- floor(min(GM.int.FP$lon))
LongMax <- ceiling(max(GM.int.FP$lon))
LatMin <- floor(min(GM.int.FP$lat))
LatMax <- ceiling(max(GM.int.FP$lat))
background <- raster(xmn = LongMin, xmx = LongMax,
                     ymn = LatMin, ymx = LatMax,
                     resolution = raster.res)
grid.ctr <- GM.int.FP[,.(lon,lat)]
rst <- rasterize(grid.ctr, background, fun = mean,
                 field = GM.int.FP[,.(value)])
writeRaster(rst, filename = file.path(US.Eng.dir, data.dir,'maps',paste0(event.name,'SA3.from.Footprint.',today,'.img')),
            format = 'HFA',overwrite = T)
}
```

```{r fp.based.SA3.Map, fig.width=12,fig.height=8,warning=F}
if(include.GM){
  m <- leaflet()
  m <- addProviderTiles(map = m, provider = 'Stamen.TonerLite',
                        group = 'Toner Lite')
  m <- addTiles(map = m, group = 'OSM')
  m <- addProviderTiles(map = m, provider = 'MapQuestOpen.Aerial',group='Aerial')

  v <- values(rst)
  v <- v[!is.na(v)]
  pal <- colorBin(palette = c('#E7E739','#006121'), domain = range(v), bins=6)
  m <- addRasterImage(map = m, rst, colors = pal, opacity = 0.5, group = 'SA3')

  m <- addPolygons(map=m, data=rupture.srdf, weight = 2, 
                   fill=F, color = 'darkblue',
                   popup=paste0('Segment: ',rupture.srdf$segment))
  m <- addLayersControl(map = m, baseGroups = c("Aerial","Toner Lite","OSM"), 
                        overlayGroups = c('SA3'),
                        options = layersControlOptions(collapsed = FALSE))

  m <- addLegend(map = m, 
                 position = "bottomleft", pal = pal, 
                 values = range(v), opacity = 1,
                 title = 'Sa 3.0s, g')
  m 
}
```

